Using cosmic variance to constrain the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1

### 2013-03-26 paper/ms.tex
some changes in the correlation section and correlation plots were changed to pdf

Next we group these $210$ mock fields in three different ways to
construct the LAEs number density distribution. The first way we
follow the observational setup and constructs $15$ different mock
surveys, each one composed of $12$ mock fields, out of which $7$
correspond to contiguous sub-boxes in the simulation to mimick the
whole SSA22, $3$ are also contiguous between them but not to the first
$7$ fields to mimick the SXDS fields and finally $2$ non-contiguous
fields that correspond to the SDF and GOODS-North fields. This will
produce $15$ different distributions for the number density for a
given model ${\mathrm M}$. The second is similar to the first
one. There aare $15$ different mock surveys with $12$ mock fields
each, but this time each field corresponds to uncorrelated sub-boxes
in the simulation. The third way in only has $1$ mock survey
containing all the $210$ mock fields, in this setup there is only one
predicted number density distribution for each model ${\mathrm M}$

@@

\subsection{Estimating the Galaxy Bias from the Halo Masses}
Using the results from the previous sections it is possible to infre
the bias of $z\sim 3$ LAEs. Considering a number of $N_{\rm fields}$
the expected number density of galaxies around the region located at
$x_{i}$ is $n_{i}=\bar{n}[1+ b\delta_{\rm DM}(x_{i})]$, where
$\bar{n}$ is the average galaxy number density and $\delta_{\rm
  DM}\equiv (\rho - \bar{\rho})/\bar{\rho}$ is the matter overdensity
in the field [REF robertson].

We calculate the bias for each mock catalog in the best models using
the corresponding dark matter overdensity in the simulation. This
results in a distribution of bias values for each model. The results
for this calculation are presented in Figure XX.  We compare this
resul agains the following estimation $b^{2}\sim {\sigma_{N}^{2} -
  \bar{N}}/\bar{N}^{2}\sigma_{\rm DM}^{2}$, where $\bar{N}$ is the
average number counts in the $N_{fields}$, $\sigma_{N}$ is their
dispersion and $\sigma_{DM}$ is the matter variance over many survey
volumes.

@@

We calculate the angular correlation function (ACF) for the best
models for a mock survey with a total surface area equal to the full
survey by Yamada et al 2012. We compare these results with the
observed ACF reported by Gawiser et al. XXX.

\begin{figure}
\begin{center}
\includegraphics[width=1.00\linewidth,angle=0]{./plots/correlation_best_models_with_obs_comp.png} 
\end{center} 
\caption{ \label{figure:landscape} 
}
\end{figure}

>>>>

Next we group these $210$ mock fields in three different ways to
construct the LAEs number density distribution. The first way (match method) we
follow the observational setup and constructs $15$ different mock
surveys, each one composed of $12$ mock fields, out of which $7$
correspond to contiguous sub-boxes in the simulation to mimick the
whole SSA22, $3$ are also contiguous between them but not to the first
$7$ fields to mimick the SXDS fields and finally $2$ non-contiguous
fields that correspond to the SDF and GOODS-North fields. This will
produce $15$ different distributions for the number density for a
given model ${\mathrm M}$. The second (random method) is similar to the first
one. There aare $15$ different mock surveys with $12$ mock fields
each, but this time each field corresponds to uncorrelated sub-boxes
in the simulation. The third (full method) way in only has $1$ mock survey
containing all the $210$ mock fields, in this setup there is only one
predicted number density distribution for each model ${\mathrm M}$

@@

\subsection{Estimating the Galaxy Bias from the Halo Masses}
Using the results from the previous sections it is possible to infer
the bias of $z\sim 3$ LAEs. Considering a number of $N_{\rm fields}$
the expected number density of galaxies around the region located at
$x_{i}$ is $n_{i}=\bar{n}[1+ b\delta_{\rm DM}(x_{i})]$, where
$\bar{n}$ is the average galaxy number density and $\delta_{\rm
  DM}\equiv (\rho - \bar{\rho})/\bar{\rho}$ is the matter overdensity
in the field [REF robertson].

We calculate the bias for each mock catalog in the best models using
the corresponding dark matter overdensity in the simulation. This
results in a distribution of bias values for each model. The results
for this calculation are presented in Figure XX.  We compare this
result against the following estimation $b^{2}\sim {\sigma_{N}^{2} -
  \bar{N}}/\bar{N}^{2}\sigma_{\rm DM}^{2}$, where $\bar{N}$ is the
average number counts in the $N_{fields}$, $\sigma_{N}$ is their
dispersion and $\sigma_{DM}$ is the matter variance over many survey
volumes.

@@

We calculate the mean angular correlation function (ACF) for the best
models for a mock survey using the match and random methods with 
two different surface areas: $1)$ the full survey (12 subfields) and
$2)$  e SSA22 field (7 subfields) reported by Yamada et al 2012 
(see section XX) . The results for these calculations  are shown 
in figure \ref{figure:correlation_match} (match) and figure
\ref{figure:correlation_random} (random).  The error bars in these figure
represent the standard deviation of the ACF over the subfields.

We compare these results with the observed ACF in the SSA22 field reported by Hayashino et al. 2004 .

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/match_full_correlation_selected_models.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plot/match_large_correlation_selected_models.pdf}\\
\end{center} 
\caption{ mean ACFs over the 7 subfields of the SSA22 field and their correponding standard deviation (error bars)
some selected models in different mass ranges. \label{figure:correlation_match} }

\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/random_full_correlation_selected_models.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plot/random_large_correlation_selected_models.pdf}\\
\end{center} 
\caption{ mean ACFs over the 7 subfields of the SSA22 field and their correponding standard deviation (error bars)
some selected models in different mass ranges. \label{figure:correlation_match} }

\end{figure*}
